draft

### 2020-02-26 src/draft.Rmd
added draft template
aggregated assessment and tax by year and municipality

1. read the data and aggregate them
```{r}
tax_pct<-read_csv(here("data", "tax_pct.csv"))
assessment_pct<-read_csv(here("data", "assessment_pct.csv"))
# omit 2016
assessment_pct<-na.omit(assessment_pct)

```

>>>>

1. read the data and aggregate them
```{r}
tax_pct<-read_csv(here("data", "tax_pct.csv"))
assessment_pct<-read_csv(here("data", "assessment_pct.csv"))
# omit 2016
assessment_pct<-na.omit(assessment_pct)
assessment_pct<-assessment_pct[,-c(1)]
names(assessment_pct)[2]<-paste("Municipalities")
tax_pct<-tax_pct[,-c(1)]

```
Note: tax_pct doesn't have Maple Ridge Rural. We decide to treat Maple Ridge Rural and Maple Ridge with the same tax.

```{r}
assessment2017<-assessment_pct  %>%  filter(Year=="2017")
tax2017<-tax_pct[,1:2]
assessment2017<-assessment2017 %>% left_join(tax2017, by = c("Municipalities"))
names(assessment2017)[9]<-paste("tax")

assessment2018<-assessment_pct  %>%  filter(Year=="2018")
tax2018<-tax_pct[,c(1,3)]
assessment2018<-assessment2018 %>% left_join(tax2018, by = c("Municipalities"))
names(assessment2018)[9]<-paste("tax")

assessment2019<-assessment_pct  %>%  filter(Year=="2019")

data_final<-assessment2017 %>% full_join(assessment2018) %>% full_join(assessment2019)
write.csv(data_final, here("data","data_final.csv"))
```

2. plots
